---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missingGroupr Package

<!-- badges: start -->
<!-- badges: end -->

The goal of missingGroupr is to provide a helper function that summarizes the number of missing values in all the columns when grouped by a specified column. The function wraps `dplyr::group_by()`, `dplyr::summarize()`, `dplyr::across()`, and `dplyr::everything()` to compute missing-value counts. 

## Installation

You can install the development version of missingGroupr from [GitHub](https://github.com/stat545ubc-2025/missingGroupr) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2025/missingGroupr")
```

## Examples

This example computes the number of missing values in the `airquality` dataset grouped by the `Month` column.

```{r example1}
missingGroupr::count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function.

```{r example2}
airquality |> missingGroupr::count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples.

```{r example3}
missingGroupr::count_all_missing_by_group(airquality, Month, .groups = "keep")
```

